Structured Genealogy Processes

### 2022-02-01 ms.Rnw
geneal trans prob updates

All cases can be categorized into four groups based on the occurrence of population event within time $\halfopen{a_q,s_q}$: no population event or simultaneous events, a birth from Deme $j$ to $j'$, a sample of Deme $j'$, and a migration from Deme $j$ to $j'$ where $j\neq j'$. Within each group, we investigate $\phi_{qk}^{j''}$ by considering whether the corresponding population event was presented in the pruned genealogy and involving the $q$-th lineage sample, which was in Deme $j''$. For $q>1$, we then have:

@@

    % B2C: either j''=j' or j''=j, the numerator = 1 when j'!=j and =2 when j'=j.
    \frac{1+\delta_{j,j'}}{I_k^{j}(I_k^{j'}-\delta_{j,j'})-\ell_{qk}^j(\ell_{qk}^{j'}-\delta_{j,j'})}, &\text{if}\ t_k=a_q\in\Cset^{j,j'}(\Och_q),\\[12pt]
    1-\frac{(1+\delta_{j,j'})\ell_{qk}^{j}}{I_k^{j}(I_k^{j'}-\delta_{j,j'})-\ell_{qk}^j(\ell_{qk}^{j'}-\delta_{j,j'})}-\frac{1}{I_k^{j'}-\ell_{qk}^{j'}}, &\text{if}\ t_k\in(a_q,s_q),\ t_k\notin\Zset^{j,j'}(\Och_q),\ \text{and}\ u_k\in\Bset^{j,j'},\\[12pt]
    0, &\text{otherwise}.
  \end{cases}
\end{equation}

>>>>

All cases can be categorized into four groups based on the occurrence of population event within time $\halfopen{a_q,s_q}$: no population event or simultaneous events, a birth from Deme $j$ to $j'$, a sample of Deme $j'$, and a migration from Deme $j$ to $j'$ where $j\neq j'$. Within each group, we investigate $\phi_{qk}^{j''}$ by considering whether the corresponding population event was presented in the pruned genealogy and involving the $q$-th lineage sample, which was in Deme $j''$ at time $t_k$. For $q>1$, we then have:

@@

    % B2C: either j''=j (in Z_{q-1} or j''=j' (not in Z_{q-1})
    % the numerator = 1 when j'!=j and =2 when j'=j.
    \frac{(1+\delta_{j,j'})}{I_k^{j}(I_k^{j'}-\delta_{j,j'})-\ell_{qk}^j(\ell_{qk}^{j'}-\delta_{j,j'})}, &\text{if}\ t_k=a_q\in\Cset^{j,j'}(\Och_q),\\[12pt]
    1-\frac{(1+\delta_{j,j'})\ \ell_{qk}^{j}\ \delta_{j',j''}}{I_k^{j}(I_k^{j'}-\delta_{j,j'})-\ell_{qk}^j(\ell_{qk}^{j'}-\delta_{j,j'})}-\frac{\delta_{j',j''}}{I_k^{j'}-\ell_{qk}^{j'}}, &\text{if}\ t_k\in(a_q,s_q),\ t_k\notin\Zset^{j,j'}(\Och_{q-1})\cup\Zset^{j,j'}(\Och_q),\ \text{and}\ u_k\in\Bset^{j,j'},\\[12pt]
    1-\frac{\delta_{j,j''}}{I_k^{j}I_k^{j'}-\ell_{qk}^j\ell_{qk}^{j'}}, &\text{if}\ t_k\in(a_q,s_q),\ t_k\in\Zset^{j,j'}(\Och_{q-1})\setminus\Zset^{j,j'}(\Och_q),\ \text{and}\ u_k\in\Bset^{j,j'},\\[12pt]
    0, &\text{otherwise}.
  \end{cases}
\end{equation}
